# Control flow {.unnumbered}

```{r}
#| label: common.R
#| eval: true 
#| echo: false
source("common.R")
```

I'll load the [`lobstr`](https://lobstr.r-lib.org/index.html), [`waldo`](https://www.tidyverse.org/blog/2020/10/waldo/), and [`purrr`](https://purrr.tidyverse.org/) packages for this chapter.

```{r}
#| eval: true 
#| code-fold: show
#| code-summary: 'install packages'
#| message: false 
#| warning: false 
#| results: hide
renv::install("lobstr")
renv::install("waldo")
renv::install("purrr")
renv::install("sloop")
library(lobstr)
library(waldo)
library(purrr)
library(sloop)
```

# Choices

## Q1

:::: {.callout-note collapse="false"}
#### Q:1

::: {style="font-size: 1.10em;"}
***What type of vector does each of the following calls to `ifelse()` return?***
:::

```{r}
#| code-fold: false
ifelse(TRUE, 1, "no")
ifelse(FALSE, 1, "no")
ifelse(NA, 1, "no")
```
::::

:::: {.callout-tip collapse="false"}
#### A1

::: {style="font-size: 1.10em;"}
*`ifelse()` is strict when it comes to the `type` (or `mode`) in the results of `tests`, because it returns a "value with the same shape as test"*
:::

```{r}
ifelse(test = TRUE, yes = 1, no = "no")
mode(TRUE)
```

This is essentially saying the test result is `FALSE`, so it evaluates to 'no'

```{r}
# the 'shape' of the test here is FALSE, so 'no' is returned 
ifelse(FALSE, 1, "no")
```

I can confirm this with `isFALSE(FALSE)`:

```{r}
# no = return values for false elements of test
ifelse(test = isFALSE(FALSE), yes = 1, no = "no")
```

"***Missing values in test give missing values in the result.**s*"

```{r}
# the 'shape' of this test is missing, so it returns missing
ifelse(test = NA, 1, "no")
# but this will work!
ifelse(test = is.na(NA), 1, "no")
```
::::

## Q2

:::: {.callout-note collapse="false"}
#### Q:2

::: {style="font-size: 1.10em;"}
***Why does the following code work?***
:::

```{r}
#| code-fold: false
#| eval: false
x <- 1:10
if (length(x)) "not empty" else "empty"

x <- numeric()
if (length(x)) "not empty" else "empty"
```
::::

:::: {.callout-tip collapse="false"}
#### A2

::: {style="font-size: 1.10em;"}
*I've rewritten this to make the conditions a little easier to see*

```{r}
#| code-fold: false
x <- 1:10
if (length(x)) {
  "not empty" 
  } else {
  "empty" 
  }
```

```{r}
#| code-fold: false
x <- numeric()
if (length(x)) {
  "not empty" 
  } else {
  "empty"
  }
```

*The answer can be found by passing both statements to `length(x) == 0`, because at bottom, this is what logical statements contain:*

```{r}
sum(TRUE)
sum(FALSE)
```

```{r}
x <- 1:10
length(x) == 0
```

```{r}
x <- numeric()
length(x) == 0
```

*So if the length of an empty numeric vector equals `0`, it's not empty*
:::
::::

# Loops

## Q1

:::: {.callout-note collapse="false"}
#### Q:1

::: {style="font-size: 1.10em;"}
***Why does this code succeed without errors or warnings?***

```{r}
#| code-fold: false 
#| eval: true
x <- numeric()
out <- vector("list", length(x))
for (i in 1:length(x)) {
  out[i] <- x[i]^2
}
out
```
:::
::::

:::: {.callout-tip collapse="false"}
#### A1

::: {style="font-size: 1.10em;"}
*The answer is explained by the objects going into the loop:*

```{r}
#| code-fold: false
x <- numeric()
out <- vector("list", length(x))
x
out
```

*Both of these are empty, and if we check what the index `i` is going to be doing inside the `for` loop, we see the following:*

-   *When we square the element at an empty numeric vector (i.e, `x[0]`), we see it's identical to the empty vector*

    ```{r}
    #| code-fold: false
    x[0]^2
    ```

-   *And if we check \``1:length(x)` we see the following:*

    ```{r}
    #| code-fold: false
    1:length(x)
    ```

-   *This means we'll have two iterations in the `for` loop. At position `[0]`, `out` is an empty `list()`*

    ```{r}
    #| code-fold: false
    out[0]
    ```

-   *And `x[0]^2` is `numeric(0)`*

    ```{r}
    #| code-fold: false
    x[0]^2
    ```

-   *So if we assign `numeric(0)` to an empty `list()` we get...*

    ```{r}
    #| code-fold: false
    out[0] <- x[0]^2
    out
    ```

-   *We get the same empty `list()`, and at position `x[1]`, it's still missing (`NA`):*

    ```{r}
    #| code-fold: false
    x[1]^2
    ```

-   *So if we view a couple of iterations, we see why `out` is `NA`*:

    ```{r}
    #| code-fold: false
    out[0] <- x[0]^2
    out
    out[1] <- x[1]^2
    out
    ```
:::
::::

## Q2

:::: {.callout-note collapse="false"}
#### Q:2

::: {style="font-size: 1.10em;"}
***When the following code is evaluated, what can you say about the vector being iterated?***

```{r}
#| code-fold: false 
#| eval: true
xs <- c(1, 2, 3)
for (x in xs) {
  xs <- c(xs, x * 2)
}
xs
```
:::

::::

:::: {.callout-tip collapse="false"}

#### A2

::: {style="font-size: 1.10em;"}
*The vector being iterated (`xs`) has three elements (`1,2,3`) and its placement inside `c()` means each element is multiplied by `2` in the loop (adding one new element to `xs`* at each iteration).

```{r}
#| code-fold: false
xs <- c(1, 2, 3)
# iteration 1
x <- 1 * 2
xs[4] <- x
xs
```

```{r}
#| code-fold: false
# iteration 2
x <- 2 * 2
xs[5] <- x
xs
```

```{r}
#| code-fold: false
# iteration 3
x <- 3 * 2
xs[6] <- x
xs
```

:::

::::

## Q3

::: {.callout-note collapse="false"}
#### Q:3

::: {style="font-size: 1.10em;"}
***What does the following code tell you about when the index is updated?***

```{r}
#| code-fold: false 
#| eval: true
for (i in 1:3) {
  i <- i * 2
  print(i) 
}
```
:::
:::
