# Why? {.unnumbered}

```{r}
#| label: common.R
#| eval: true 
#| echo: false
source("common.R")
```

This is yet *another* version of the solutions to [Advanced R, 2nd edition](https://adv-r.hadley.nz/) (`advR2`). I've returned to `advR2` more than any other resource for my day-to-day activities as an R developer. After working through each of the exercises, then reading how others had solved them, I decided some the approaches I took to solving the exercises differed enough to warrant putting them into a book. 

I highly recommend the [Advanced R Solutions](https://advanced-r-solutions.rbind.io/) by Malte Grosser, Henning Bumann, and Hadley Wickham. I'll refer to these solutions in the following callout box:

::: {.callout-caution collapse="true"}

#### Answer: advRs 2021

:::

Indrajeet Patil also has a [solutions manual](https://bookdown.org/IndrajeetPatil/Advanced-R-exercises/) worth reading for alternative approaches. I'll refer to these solutions in the following callout box

:::: {.callout-warning collapse="true"}

#### Answer: advRs 2022

:::

## Helper functions

After reading the [functions chapter of `advR2`](https://adv-r.hadley.nz/functions.html), I wrote some helper functions for various chapters: 

## Object info

1. `obj_info()` combines base functions for `class()`, `typeof()`, `attributes()` along with functions from `lobstr` and `sloop`.

-   `obj_info()` works with functions and function outputs:

    ```{r}
    #| code-fold: true
    obj_info(x = Sys.time())
    obj_info(x = Sys.time)
    ```

-   `obj_info()` and replacement, assignment, arithmetic, and matching operators:

    ```{r}
    #| code-fold: true
    obj_info(x = `[`)
    obj_info(x = `<-`)
    obj_info(x = `-`)
    obj_info(x = `%in%`)
    ```

-   `obj_info()` and vectors:

    ```{r}
    #| code-fold: true
    obj_info(1:10)
    obj_info(mtcars$mpg)
    x <- factor(x = LETTERS[1:3], 
             levels = LETTERS[1:3], 
             labels = LETTERS[1:3])
    obj_info(x = x)
    ```


These helper functions are stored in the `common.R` script. 