# Names & Values {.unnumbered}

```{r}
#| label: common.R
#| eval: true 
#| echo: false
source("common.R")
```

I'll load the [`lobstr`](https://lobstr.r-lib.org/index.html), [`waldo`](https://www.tidyverse.org/blog/2020/10/waldo/), and [`purrr`](https://purrr.tidyverse.org/) packages for this chapter.

```{r}
#| eval: true 
#| code-fold: show
#| code-summary: 'install packages'
#| message: false 
#| warning: false 
#| results: hide
renv::install("lobstr")
renv::install("waldo")
renv::install("purrr")
renv::install("sloop")
library(lobstr)
library(waldo)
library(purrr)
library(sloop)
```

# Exercises: Binding basics

## Q:1

:::: {.callout-note collapse="false"}
#### Q:1

::: {style='font-size: 1.10em;'}
***Explain the relationship between `a`, `b`, `c` and `d` in the following code:***
:::

```{r}
#| code-fold: false
a <- 1:10
b <- a
c <- b
d <- 1:10
```


::::


:::: {.callout-tip collapse="false"}
#### A:1

::: {style='font-size: 1.10em;'}
`a` and `d` are vectors with the same values, but different memory locations. I use `waldo::compare()` because it has prettier printing for differences:
:::

```{r}
#| code-fold: true 
#| code-summary: 'show A1'
waldo::compare(
  x = lobstr::obj_addr(x = a), 
  y = lobstr::obj_addr(x = b))

waldo::compare(
  x = lobstr::obj_addr(x = a), 
  y = lobstr::obj_addr(x = c))

waldo::compare(
  x = lobstr::obj_addr(x = b), 
  y = lobstr::obj_addr(x = c))

waldo::compare(
  x = lobstr::obj_addr(x = a), 
  y = lobstr::obj_addr(x = d))
```

::::

## Q:2 



:::: {.callout-note collapse="false"}
#### Q:2

::: {style='font-size: 1.10em;'}
***The following code accesses the mean function in multiple ways. Do they all point to the same underlying function object? Verify this with `lobstr::obj_addr()`.***
:::

```{r}
#| code-fold: false 
#| eval: false
mean
base::mean
get("mean")
evalq(mean)
match.fun("mean")
```


::::

:::: {.callout-tip collapse="false"}
#### A2

::: {style='font-size: 1.10em;'}
I used my `get_info()` function to verify these are all S3 generic functions from the `base` package, so they all share the same underlying function object.
:::

```{r}
#| code-fold: true 
#| code-summary: 'check with get_info()'
obj_info(mean)
obj_info(base::mean)
obj_info(get("mean"))
obj_info(evalq(mean))
obj_info(match.fun("mean"))
```

:::

Both solutions manuals solve this problem the same way (with `list()` and `unique()`):

:::: {.callout-warning collapse='true'}

#### Answer advRs 2021:

::: {style='font-size: 1.10em;'}
*Yes, they point to the same object. We confirm this by inspecting the address of the underlying function object.*
:::

```{r}
mean_functions <- list(
  mean,
  base::mean,
  get("mean"),
  evalq(mean),
  match.fun("mean")
)

unique(obj_addrs(mean_functions))
```

::::



:::: {.callout-caution collapse='true'}

#### Answer advRs 2022 A:2

::: {style='font-size: 1.10em;'}
*All listed function calls point to the same underlying function object in memory, as shown by this object’s memory address:*
:::

```{r}
obj_addrs <- obj_addrs(list(
  mean,
  base::mean,
  get("mean"),
  evalq(mean),
  match.fun("mean")
))

unique(obj_addrs)
```

::::


:::: {.callout-note collapse="false"}

#### Q3

::: {style='font-size: 1.10em;'}

***By default, base R data import functions, like `read.csv()`, will automatically convert non-syntactic names to syntactic ones. Why might this be problematic? What option allows you to suppress this behaviour?***

:::

::::


:::: {.callout-note collapse="false"}

#### Q4

::: {style='font-size: 1.10em;'}

***What rules does `make.names()` use to convert non-syntactic names into syntactic ones?***

:::

::::

:::: {.callout-note collapse="false"}

#### Q5

::: {style='font-size: 1.10em;'}

***I slightly simplified the rules that govern syntactic names. Why is `.123e1` not a syntactic name? Read `?make.names` for the full details.***

:::


::::